A large leading tail of atmospheric escape in the HAT-P-67 b system

### 2023-02-14 paper/paper1/ms.tex
Discussion sections

\subsection{Size and geometry of atmospheric escape}
Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.  The excess occurs as early as 30\% of the orbital path.  That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.  We are therefore primarily detecting gas that is entirely unbound from the planet.  The leading gas tail does not appear to accelerate, neither blue-shifting nor redshifting.   The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.  Such a scenario may arise from preferential emission on the planet dayside, or other configurations that we discuss in Section \ref{secDiscuss}.

@@

>>>>

\subsection{Size and geometry of outflow}
Helium absorption occurs predominantly before the planet is in-transit, indicating a \emph{leading} tail escaping the planet.  The excess occurs as early as 30\% of the orbital path.  That large fraction of an orbit translates to about 0.1 AU, 130 planetary radii, and well outside of the Roche Lobe, with its Hill radius of merely 2.6 planetary radii.  We are therefore primarily detecting gas that is entirely unbound from the planet.  The leading gas tail does not appear to accelerate, neither blue-shifting nor redshifting.   The bulk of the detectable unbound gas may therefore follow its own Keplerian trajectory at a slightly shorter period orbit, pulling away from the planet parallel to the orbital path.  Such a scenario may arise from preferential emission on the planet dayside, or other configurations that we discuss in Section \ref{secDiscuss}.

@@

\subsection{Cause for stellar modulation}
The \emph{TESS} lightcurve exhibits up to $0.36\%$ peak-to-valley modulation amplitude, with a characteristic timescale of $p=4.8-5.2$ days, and with some sectors exhibiting lower amplitudes of modulation.  The baseline interpretation would consign these cyclical modulations to the familiar stellar activity: surface features---either starspots, faculae, or plage---entering and exiting the projected stellar disk on the stellar rotation period comparable to the 4.8 day orbital period of planet b.  The cause for such orbital and rotational synchronization would then ostensibly be tides.  We examine the prospect of tides in the next subsection.

Instead, the exteme mass loss and credibility of the ohmic diffusion model motivates the prospect of star-planet-interaction (SPI) that we consider now.  In this scenario, the magnetic field of the planet permeates the space between the star and planet.  Magnetic perturbations propagate via planetary magnetic fields with the Alfv\'en speed.  The planet can interact with the star if the Alfv\'en speed exceeds the stellar wind speed controling the bulk motion of intervening medium.  The magnetic field of the planet is not known, but the ohmic dissipation mechanism favors a limited range in the magnetic field strength: large enough to cause significant dissipative energy generation, but not too large to shut down motion entirely.  \citet{2011ApJ...738....1B} estimate this range as between about 1-30 Gauss.  With

A few observations disfavor this interpretation.  First, the non-detection of variability in the \ion{Ca}{2} H and K lines and H~$\alpha$ lines.

\subsection{Timescale for tidal synchronization}
